Spin canonical divisors of log stacky curves

### 2015-06-28 stacky_write_up/spin_cring.tex
merged

\noindent
\todo{why is there no floor in the above equation, as in ~\ref{eqn:deg1_sat_ind_dim}} so in $H^0 (X, \lfloor d\halfcan \rfloor)$ we can find elements with pole
order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
\beta} \rfloor \}$. We will use positive best lower approximations to
construct the generators $\{y_i\}$ as described in the lemma's statement.

>>>>

\noindent
so in $H^0 (X, \lfloor d\halfcan \rfloor)$ we can find elements with pole
order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
\beta} \rfloor \}$. We will use positive best lower approximations to
construct the generators $\{y_i\}$ as described in the lemma's statement.
